\reportsection{Binding}
\label{sec:binding}

\subsection{Definition and Failure}
\label{sec:binding-def}

\begin{definition}[Position binding]\label{def:vc-binding}
$\VC$ is \emph{position binding} if no efficient adversary outputs a commitment
$\comm$ with two accepted openings
$(\idxset_b,\MTMessageSubVector_b,\opening_b)$ that disagree at some
$i\in\idxset_0\cap\idxset_1$, except with probability $\negl$.  The commitment
has no honest-generation requirement.  A single conflict at a shared index is
the local witness that binding has failed.
\end{definition}

\paragraph{One conflict is the whole failure.}
Position binding is what lets a soundness argument treat each queried answer as
the unique value the commitment fixes the moment $\comm$ is published, before
the query set is chosen.

\subsection{Sizing and Validation}
\label{sec:binding-valid}

\paragraph{Two adversary models, two digest targets.}
The concrete-security accounting behind the digest floor is the
worst-case-versus-average-case split of~\cite{CY26}: at $\secpar=128$, binding
against a worst-case adversary needs a $383$-bit output, while the average-case
notion needs $255$ bits, a roughly $1.5\times$ gap.  The grinding discussion of
\cref{sec:background} is that worst-case notion stated operationally, because a
grinding prover is exactly one who spends its whole query budget hunting for
the transcript where the bound is tightest.

\paragraph{The rule prices both, through $h$.}
The rule (\cref{eq:rule}) sets the digest to $D=9$ field elements
($\digestbits=270$ bits) for BabyBear at $\secpar=128$, $h=64$: a $13$-bit
margin over the $\secpar+1+2h=257$-bit floor, which is the average-case
instance.  The worst-case target enters the rule only through the query
budget $h$, the declared input that names the adversary model.  Re-running
the constructor at $h=128$ gives
$D=\lceil(128+1+256)/30\rceil=13$, so $\digestbits=390\ge383$, with no new
analysis.  $D=9$ and $D=13$ are two certificates for two adversary models and
must not be crossed: a $D=9$ configuration certifies nothing against a
grinding prover.  Write $\ThetaVC$ for the concrete
configuration under test (field, level, hash, and derived widths), so
$\Adv{bind}(\ThetaVC)$ is the binding advantage against that Merkle instance.

\begin{proposition}[Binding from collision resistance]\label{thm:binding-cr}
Let $\MT[\RO]$ be a Merkle commitment over a shape $G_\ell$ whose leaf encoding
is injective and whose leaf and internal-node calls are domain separated.  If
the shared $\digestbits$-bit oracle receives at most $\querybudget$ distinct
queries during the complete experiment, then
\[
  \Adv{bind}(\ThetaVC)
  \le \Pr[\text{oracle-trace collision}]
  \le \frac{\querybudget(\querybudget-1)}{2^{\digestbits+1}},
\]
which meets $2^{-\secpar}$ when $\querybudget\le2^{h}$ and
$\secpar+1+2h\le\digestbits$.
\status{Lean-backed, generic over \texttt{MerkleShape}}
\end{proposition}

\noindent\emph{Proof sketch.}
A disputed index $i\in\idxset_0\cap\idxset_1$ yields two authentication paths
that agree at some parent but disagree below it: two distinct oracle inputs with
one output.  Domain separation pins the leaf and internal roles, so the
collision is genuine.  What remains is the adversary's freedom to re-interpret
the same digests under a different tree shape, which is the tree-inequality
event $E_{\mathrm{tree}}$ of~\cite{CY26}: the tree reconstructed from the
commitment trace and the one reconstructed after the opening queries can differ
only if some opening answer accidentally matches a label already fixed in the
first tree.  A union bound over the opening queries keeps that probability
negligible whenever the digest resists collisions, so a binding break still
reduces to one oracle collision rather than to any freedom in how the tree is
read.  Hashing a geometry tag of layer, index, and arity into each node keeps
this domain separation positional, which forecloses the replay of a subtree
proof in a differently shaped tree.

\paragraph{The reduction is generic; the backing is mechanical.}
The colliding-paths step, the birthday bound, and the parameter arithmetic
additionally carry a machine-checked Lean backing~\cite{ZLeanVC26}, so binding
is the axis with independent mechanical assurance behind it.  The reduction
itself is generic over the Merkle shape: the binary tree is the exhibited
instance, and $k$-ary and arbitrary-length shapes share the argument but are
not yet exhibited (\cref{sec:conclusion}).
