\reportsection{Conclusion and Next Steps}
\label{sec:conclusion}

A vector commitment is only as strong as the parameters underneath it, and the
default \textsf{ark-mt} configurations miss that target for small fields on
both axes at once.  This report established three things.  The rule of
\cref{eq:rule} derives, from a designer's declared inputs, the digest and salt
parameters a security target forces, and refuses the undersized configurations
the shipped defaults accept, including the one broken here in $44$ seconds.
The cost benchmarks price the derived parameters and show that for Poseidon2 the
certified configurations fit inside permutation blocks already paid for, so
correct security at $\secpar=128$ costs nothing extra.  The binding analysis
behind the rule additionally carries a machine-checked Lean backing.

\paragraph{Next.}
The formal status splits three ways, and the split is the information.  Closed:
the binding chain end to end, and the salt-cardinality lemmas hiding needs.
Scoped and believed but not yet closed: the extraction bridge and one
distributional averaging step, both reduced to named deterministic pieces.
Not yet stated in the formal model: the sampling-based hiding game and
equivocation, so the hiding claim rests on the intended reduction of
\cref{sec:hiding} rather than a checked theorem.  Beyond the formalisation,
multi-round BCS and Fiat--Shamir soundness would justify the strengthened
digest target at the protocol level, and the $k$-ary and arbitrary-length
shapes share the generic binding reduction but are not yet exhibited.
