\reportsection{Contributions}
\label{sec:contributions}

AZ - I don't think this paragraph is doing work for you. I'd probably scrap entirely
revise how you feel appropriate the new version I'm suggesting for you below.

Merkle commitments are the hash-based vector commitments that post-quantum
proving systems are compiled through, so the commitment's guarantees become the
compiled argument's guarantees.  Configuring one is subtle: the digest width
and the per-leaf salt cardinality both move with the field, and an undersized
choice still compiles and passes every functional test.  The defaults shipped
by Arkworks miss this detail, which comes to matter when working in small fields.
This project makes sizing those parameters the infrastructure's obligation
rather than the user's.  The contributions:

AZ - Merkle commitments are essential to modern proof systems, but practioners
have an unreasonable challenge of balancing security and performance in the context
of complex security definitions and extensive configuration levers. We aim to reduce
this burden on the user by lifting it into infrastructure. With this mind, we highlight
four main contributions:

AZ - I find all of these titles hard to understand. 
\begin{itemize}[itemsep=0.35\baselineskip, topsep=0.35\baselineskip]
  \item \textbf{A parametrisation function for the commitment layer}
  (\cref{sec:background,sec:spine}): for a chosen field, hash, interface, and
  adversary query budget, enter a target security level and receive the digest
  width and salt cardinalities that achieve it, or enter concrete parameters
  and receive the security level they achieve together with an estimate of
  their cost.  Computed once, reused across fields, independent of tree arity.

  AZ - What "shipped defaults"? That repo isn't published. I would probably remove this.
  \item \textbf{A demonstrated break of the shipped defaults}: the
  field-size-agnostic one-element digest publishes a BabyBear root in a
  ${\sim}30$-bit space, and a deliberate collision (one root, two accepted
  openings disagreeing at a shared index) takes $44$~seconds
  (\cref{sec:binding}); the matching one-element salt breaks hiding outright
  (\cref{sec:hiding}).

  AZ - This is probably good
  \item \textbf{A measured cost matrix} (\cref{sec:cost}): we benchmark
  prover time, verifier time, and proof size across parameter combinations
  spanning three fields and two hash families, separating security thresholds
  from cost transitions and showing that for Poseidon2 the certified
  $\secpar=128$ parameters cost nothing extra (\cref{tab:cost-at-128}).

  AZ - You can keep this but I don't really know what you mean by "appropriate ROM" maybe just pick one and keep it simple?
  \item \textbf{A machine-checked proof line}: we are developing a Lean~4
  proof~\cite{ZLeanVC26} that the derived parameters give binding and hiding
  in the appropriate random-oracle model; the parts not yet mechanised are
  either established by other means or rest on theorems already known and
  accepted in the literature.

  AZ - consolidation of optimal multiproof impl <-- you can keep this but make it very brief
  \item \textbf{A consolidation of the first semester's engineering}: the
  multiproof compression and its coordinate-encoding backing (out of scope
  here, but the groundwork for geometric binding), the interface redesign,
  and the benchmark harness built
  against the legacy \textsf{Arkworks/crypto-primitives} (\cref{sec:provenance}) are carried
  into this report, which supplies the specification that work was missing.
\end{itemize}

\noindent
AZ - Delete.
To draw the line of contribution plainly: the rule, the break, the benchmark
matrix and its harness lineage (\cref{sec:provenance}), and the formalisation
are this work.  The vector-commitment and Merkle notation and the
concrete-security accounting are~\cite{CY26}'s, and the \textsf{ark-vc} crate
design belongs to the surrounding project.
