\reportsection{Hiding}
\label{sec:hiding}

\subsection{Definition and Failure}
\label{sec:hiding-def}

\begin{definition}[Hiding]\label{def:vc-hiding}
A randomised $\VC$ whose $\Commit$ draws salts from a space $\rndspace$ is
\emph{hiding} if, for any two messages of length $\MTMessageLength$ and any
adversary that after seeing $\comm$ adaptively opens positions on which the
messages agree, the advantage in deciding which was committed is at most
$\negl$.  For Merkle this refines to \emph{root hiding}---the real root is
statistically close to one simulated without $\msgvec$---strengthened to
\emph{selective-opening hiding}, which must also hide through the disclosed
salts and authentication paths of partial openings.
\end{definition}

A Merkle salt is a random per-leaf nonce: each leaf is itself a basic commitment
$H(\msgvec_i,\text{salt})$, the salt travels in the authentication path beside
the sibling digests so the verifier can recompute the leaf, and opening one leaf
commitment under two different salts would force a hash collision, so the salt
binds a value to its position even as it hides it.  Hiding then rests entirely on
the salt space, which must be both well sampled and large enough to resist search
within the security budget; a deterministic salt satisfies neither, since the
receiver can recompute candidate leaf commitments.
The shipped one-element BabyBear salt carries only ${\sim}30$ bits and is broken
outright, and---unlike binding's additive contribution---there is no
protocol-level rescue, because the root is read from the transcript before any
later message.

\subsection{Sizing and Contract}
\label{sec:hiding-valid}

The rule sets the salt cardinality to $k=5$ field salts or $S=16$ byte salts for
BabyBear at $\secpar=128$, each defining a space of at least $2^{128}$ elements.
These cardinalities are machine-checked (\code{babyBear\_field\_salt\_hiding},
\code{babyBear\_byte\_salt\_hiding}), and the interface enforces them
structurally: \code{MerkleHasher} no longer exposes a salt sampler, and hiding
randomness must arrive through a typed, key-indexed \code{Randomness} field
consumed by a dedicated hiding commit.

What remains is an \emph{intended reduction}, not a machine-checked theorem.  The
root-hiding obligation has the form
\[
  \Adv{hide}(\ThetaVC)
  \le \frac{\msglen\querybudget}{2^{\saltbits}}
  + \varepsilon_{\mathrm{internal}}(\digestbits,\querybudget,\shape),
\]
read off two bad events: a query to a hidden salted leaf input, or an internal
hash collision as the simulation rebuilds the tree from the leaves up to the
root.  Discharging it and lifting it to the selective-opening target is the next
composition step, by way of an oracle-native leaf argument, a bottom-up
simulation of the root from the leaves, and a simulator for the full disclosed
view.  The proved salt sizes are prerequisites, not the theorem: the cardinality
lemmas are machine-checked and the composition stays an open obligation.
